\documentclass[12pt]{article}
\usepackage[left=30mm, top=0.5in, bottom=0.5in]{geometry}
\begin{document}
	
\title{\textbf{Proof of Concept Demonstration Plan}}
\author{The A Team\\ \small Ren-David Dimen, Gabriel Lopez de Leon, Jay Nguyen}
\date{02 October 2015}
\maketitle

\section*{Possible Risks}

The legacy code that our team is re-designing has improper coding structure and no proper documentation. This may pose some possible risks to the overall project. Though the program lacks proper programming architecture, implementing it should pose no problems as it is easily runnable and modifiable. The scope of the project is quite feasible as the program is simple enough to understand and parts of the code can be easily remodeled given our team's technical knowledge and past experience coding in Java. \\

Testing is an important part of the software development process and is necessary to ensure the program in question works properly and addresses all requirements. The testing for our game may prove to be somewhat difficult due to the amount of UI testing required for the main functions of the game itself. However, automated testing is still possible and necessary to test certain aspects of the code which deal with how the system works. Automated testing can be used to test functionality of the game such as how the program keeps track of the timer, the score, the state of the arena, etc. \\

Other possible risks such as portability or required libraries are not an issue with regards to our project. There are no other extra libraries needed to run the game. Portability is also not a problem as it should be able to run on any platform that can run Java. Most windows PC's should be able to easily run the program without any difficulties. \\

\section*{Overcoming the Risks}

To demonstrate that the risks can be overcome, our group plans to demonstrate a working implementation of the game. This will be done while running tests on the program to ensure that the game runs as intended; without any bugs. This will demonstrate how automated testing for our program is possible and thus overcoming the most significant risk we have for our project. Furthermore, this will reinforce the feasibility of our project while showing that it is of the proper scope and size for this course.

\end{document}